---
name: Sooyong
surname: Lee
position: "PhD"
# profilepic: "img/kate.jpeg"
address: "Educational Psychology, The University of Texas at Austin"
phone: +1 736 865 0618
# www: mariecurie.com
email: "sooyongl09@gmail.com"
# twitter: DontLookUpFilm
github: sooyongl/sylcv
# linkedin: mariecurie
aboutme: "I have recently discovered Comet Dibiasky that is approximately 10-15km in size, and based on my orbital calculations is estimated to strike Earth in 6 months and 14 days"
date: "`r format(Sys.time(), '%B %Y')`"
headcolor: 414141
output: 
  vitae::awesomecv:
    page_total: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(here)
library(tidyverse)
library(googlesheets4)
```

```{r functions}
# orcid_data <- do.call("rbind",
#   rorcid::orcid_educations("0000-0002-2140-5352")$`0000-0002-2140-5352`$`affiliation-group`$summaries
# )
# orcid_data %>%
#   detailed_entries(
#     what = `education-summary.role-title`,
#     when = glue::glue("{`education-summary.start-date.year.value`} - {`education-summary.end-date.year.value`}"),
#     with = `education-summary.organization.name`,
#     where = `education-summary.organization.address.city`
#   )

readGoogleSheets <- function(sheet_name) {
  
  cvInfo <- googlesheets4::read_sheet("https://docs.google.com/spreadsheets/d/10ye0YoRjDaCrN4nc1YiFXO8DRtVSyTg1B4z_w8icLtI/edit#gid=0", sheet = sheet_name)
  
  cvInfo
}

```

# Professional Summary

<!--  * I poisoned myself doing research. -->
<!--  * I was the first woman to win a Nobel prize -->
<!--  * I was the first person and only woman to win a Nobel prize in two different sciences. -->

This is a good opportunity to introduce yourself professionally and summarise
why your skills are well suited to the job you are applying for!


# Education
<!-- I am a Teaching Assistant in the Astronomy Department and am passionate about playing a positive role in shaping the new generation of astronomers.  -->


```{r}
# library(tibble)
# tribble(
#   ~ Degree, ~ Year, ~ Institution, ~ Where,
#   "Informal studies", "1889-91", "Flying University", "Warsaw, Poland",
#   "Master of Physics", "1893", "Sorbonne Université", "Paris, France",
#   "Master of Mathematics", "1894", "Sorbonne Université", "Paris, France"
# ) %>% 
#    detailed_entries(Degree, Year, Institution, Where)
readGoogleSheets("Education") %>% 
  detailed_entries(what = Degree,
                   when = Year,
                   with = Institution,
                   where = Location,
                   why = Details)
```

# Research experience
```{r}
readGoogleSheets("Experience") %>% 
  # filter(category == "poster") %>% 
  vitae::detailed_entries(what = Name,
                          when = Year,
                          where = Position,
                          with = note,
                          why = Desc)
```

# Language skills
```{r}
# skills %>% 
#   brief_entries(when = skill) # ,
                # with = level)
```

\newpage


# Publications

```{r}
# library(dplyr)
# knitr::write_bib(c("vitae", "tibble"), "packages.bib")
# 
# bibliography_entries("packages.bib") %>%
#   arrange(desc(author$family), issued)
# 
# bibliography_entries(here("papers.bib")) 
```

<!-- ## Another way to display publications is using R Markdown. You can also use latex commands throughout the document: -->

\setlength{\leftskip}{0cm}
**2021**

\setlength{\leftskip}{1cm}
Cory L. Cobb, Charles R. Martínez, Jr., **Sooyong Lee**, Tae Kyoung Lee, & Elma I. Lorenzo-Blanco, (2021). Acculturation trajectories differ by youth age at arrival and time in residency among Latino immigrant families in a US emerging immigrant context. *International Journal of Intercultural Relations*,  81, 79-93, DOI: [10.1016/j.ijintrel.2021.01.005](10.1016/j.ijintrel.2021.01.005).

\setlength{\leftskip}{0cm}
**2022**

\setlength{\leftskip}{1cm}
**Sooyong Lee** & Tiffany A. Whittaker, (2022). Comparison of Three Approaches to Class Enumeration in Growth Mixture Modeling when Time Structures are Variant Across Latent Classes. *Structural Equation Modeling: A Multidisciplinary Journal*,  29,	23-35, DOI:[10.1080/10705511.2021.1956320](10.1080/10705511.2021.1956320).


Seung Choi, Sangdon Lim, Luping Niu, **Sooyong Lee**, Christina M. Schneider, Jay Lee, & Garron J.	(2022).	maat: An R Package for Multiple Administrations Adaptive Testing.	*Applied Psychological Measurement*,	46-1,	73-74, DOI:[10.1177/01466216211049212](10.1177/01466216211049212).

**Sooyong Lee**, Suhwa Han, & Seung W. Choi	(2022).	DIF Detection With Zero-Inflation Under the Factor Mixture Modeling Framework. *Educational and Psychological Measurement*,	82-4,	678-704, DOI:[10.1177/00131644211028995](10.1177/00131644211028995).

**Sooyong Lee** & Tiffany A. Whittaker (2022). Parallel Process Latent Growth Modeling with Multivariate Confounders/Suppressors. *Structural Equation Modeling: A Multidisciplinary Journal*, DOI:[10.1080/10705511.2022.2133774](10.1080/10705511.2022.2133774).

**Sooyong Lee**, Kahyun Lee, & Tiffany A. Whittaker	(2022). Application of Associative Discrete-Time Survival Analysis Using Latent Transition Specification. *Structural Equation Modeling: A Multidisciplinary Journal*, DOI: [10.1080/10705511.2022.2138892](10.1080/10705511.2022.2138892)

\setlength{\leftskip}{0cm}
**2023**


**Sooyong Lee**, Adam Sales, Hyeon-Ah Kang, & Tiffany A. Whittaker (2023).	Fully-Latent Principal Stratification. *The Annual Meeting of the Psychometric Society* (in print)


# Program

```{r}
readGoogleSheets("Publication") %>% 
  filter(category == "software") %>% 
  vitae::detailed_entries(what = title,
                          when = year,
                          # where = Location, 
                          # why = Details,
                          with = author
                          )
```



# Presentation

```{r}
readGoogleSheets("Presentation") %>% 
  filter(category == "poster") %>% 
  vitae::detailed_entries(what = title,
                          when = year,
                          where = Location, 
                          with = author, 
                          why = Details)
```


# Fellowship & Awards

```{r}
readGoogleSheets("Fellowship/Awards") %>% 
  # filter(category == "poster") %>% 
  vitae::detailed_entries(what = Type,
                          when = Year,
                          # where = Location, 
                          # with = author, 
                          why = Desc)
```















