%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for CV/Resume
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Author:
% Claud D. Park <posquit0.bj@gmail.com>
% http://www.posquit0.com
%
%
% Adapted to be an Rmarkdown template by Mitchell O'Hara-Wild
% 23 November 2018
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%
%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[11pt,a4paper,]{awesome-cv}

% Configure page margins with geometry
\usepackage{geometry}
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}


% Specify the location of the included fonts
\fontdir[fonts/]

% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight

\definecolor{awesome}{HTML}{414141}

% Colors for text
% Uncomment if you would like to specify your own color
% \definecolor{darktext}{HTML}{414141}
% \definecolor{text}{HTML}{333333}
% \definecolor{graytext}{HTML}{5D5D5D}
% \definecolor{lighttext}{HTML}{999999}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{true}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}

\def\endfirstpage{\newpage}

%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%-------------------------------------------------------------------------------
% Available options: circle|rectangle,edge/noedge,left/right

\name{Sooyong}{Lee}

\position{PhD}
\address{Educational Psychology, The University of Texas at Austin}

\mobile{+1 736 865 0618}
\email{\href{mailto:sooyongl09@gmail.com}{\nolinkurl{sooyongl09@gmail.com}}}
\github{sooyongl/}

% \gitlab{gitlab-id}
% \stackoverflow{SO-id}{SO-name}
% \skype{skype-id}
% \reddit{reddit-id}


\usepackage{booktabs}

\providecommand{\tightlist}{%
	\setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

%------------------------------------------------------------------------------



% Pandoc CSL macros
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{2em}
\newenvironment{CSLReferences}[3] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
  % set entry spacing
  \ifnum #2 > 0
  \setlength{\parskip}{#2\baselineskip}
  \fi
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{\honortitlestyle{#1}}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{\honordatestyle{#1}}}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

\begin{document}

% Print the header with above personal informations
% Give optional argument to change alignment(C: center, L: left, R: right)
\makecvheader

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
% 2019-02-14 Chris Umphlett - add flexibility to the document name in footer, rather than have it be static Curriculum Vitae


%-------------------------------------------------------------------------------
%	CV/RESUME CONTENT
%	Each section is imported separately, open each file in turn to modify content
%------------------------------------------------------------------------------



\hypertarget{professional-summary}{%
\section{Professional Summary}\label{professional-summary}}

I am a psychometrician with expertise in applying modern statistical
theories and techniques. My research interests are in the development
and application of statistical models such as such as structural
equation modeling (SEM), multilevel modeling (MLM), and item response
theory (IRT). Recently, I have focused on Bayesian estimation to model
the relationships among variables.

\hypertarget{education}{%
\section{Education}\label{education}}

\begin{cventries}
    \cventry{Ph.D.}{The University of Texas at Austin}{Austin, Texas}{2017-Present}{\begin{cvitems}
\item Major in Quantitative Methods
\end{cvitems}}
    \cventry{M.A.}{Korea University}{Seoul, Republic of Korea}{2014-2017}{\begin{cvitems}
\item Major in Educational Statistics and Measurement
\end{cvitems}}
\end{cventries}

\hypertarget{research-experience}{%
\section{Research experience}\label{research-experience}}

\begin{cventries}
    \cventry{}{CGS PhD Career Pathways project}{Graduate Research Assistant}{2018/9-2019/5}{\begin{cvitems}
\item Data analysis for surveys to collect data on the career pathways of past and present STEM and humanities PhD students.
\end{cvitems}}
    \cventry{President's Award for Global Learning (PAGL)}{President's Award for Global Learning (PAGL)}{Graduate Research Assistant}{2019/1-2019/8}{\begin{cvitems}
\item Designing a culturally appropriate mobile application to increase mental health literacy and self-care habits among South Korean young adults
\end{cvitems}}
    \cventry{}{COE Full-Time Tenured and Tenure-Track Faculty}{Graduate Research Assistant}{2019/9-2019/12}{\begin{cvitems}
\item Data analysis for surveys of graduate programs of education at the Univerisity of Texas at Austin
\end{cvitems}}
    \cventry{Northwest Evaluation Association (NWEA)}{MAAT package development project}{Graduate Research Assistant}{2019/9-2020/5}{\begin{cvitems}
\item Development of MAAT package for Computerized Adaptive Testing for Northwest Evaluation Association (NWEA)
\end{cvitems}}
    \cventry{IES grant}{FLPS project}{Graduate Research Assistant}{2021/9-Present}{\begin{cvitems}
\item Development of FLPS package for Fully-latent Principal Stratification
\end{cvitems}}
    \cventry{Creative Measurement Solutions LLC}{Embedded Standard Setting (ESS)}{Intern}{2020/6-2020/8}{\begin{cvitems}
\item Internship for developing Shiny app for Embeded Standard Setting
\end{cvitems}}
    \cventry{Creative Measurement Solutions LLC}{Embedded Standard Setting (ESS)}{Intern}{2021/6-2020/8}{\begin{cvitems}
\item Internship for developing ESS package for Embeded Standard Setting
\end{cvitems}}
\end{cventries}

\hypertarget{teaching-experience}{%
\section{Teaching experience}\label{teaching-experience}}

\begin{cventries}
    \cventry{Professor Tiffany Whittaker}{EDP 380C: Structural Equation Modeling}{Teaching Assistant}{2020/1-2020/5}{}\vspace{-4.0mm}
    \cventry{Professor Tiffany Whittaker}{EDP 380C: Structural Equation Modeling}{Teaching Assistant}{2021/1-2021/5}{}\vspace{-4.0mm}
\end{cventries}

\hypertarget{publications}{%
\section{Publications}\label{publications}}

\setlength{\leftskip}{0cm}

\textbf{2021}

\setlength{\leftskip}{0.5cm}

\hangindent=2em \hangafter=1 Cory L. Cobb, Charles R. Martínez, Jr.,
\textbf{Sooyong Lee}, Tae Kyoung Lee, \& Elma I. Lorenzo-Blanco, (2021).
Acculturation trajectories differ by youth age at arrival and time in
residency among Latino immigrant families in a US emerging immigrant
context. \emph{International Journal of Intercultural Relations}, 81,
79-93.

\setlength{\leftskip}{0cm}

\textbf{2022}

\setlength{\leftskip}{0.5cm}

\hangindent=2em \hangafter=1 \textbf{Sooyong Lee} \& Tiffany A.
Whittaker, (2022). Comparison of Three Approaches to Class Enumeration
in Growth Mixture Modeling when Time Structures are Variant Across
Latent Classes. \emph{Structural Equation Modeling: A Multidisciplinary
Journal}, 29, 23-35.

\hangindent=2em \hangafter=1 Seung Choi, Sangdon Lim, Luping Niu,
\textbf{Sooyong Lee}, Christina M. Schneider, Jay Lee, \& Garron J.
(2022). maat: An R Package for Multiple Administrations Adaptive
Testing. \emph{Applied Psychological Measurement}, 46-1, 73-74.

\hangindent=2em \hangafter=1 \textbf{Sooyong Lee}, Suhwa Han, \& Seung
W. Choi (2022). DIF Detection With Zero-Inflation Under the Factor
Mixture Modeling Framework. \emph{Educational and Psychological
Measurement}, 82-4, 678-704.

\hangindent=2em \hangafter=1 \textbf{Sooyong Lee} \& Tiffany A.
Whittaker (2022). Parallel Process Latent Growth Modeling with
Multivariate Confounders/Suppressors. \emph{Structural Equation
Modeling: A Multidisciplinary Journal}.

\hangindent=2em \hangafter=1 \textbf{Sooyong Lee}, Kahyun Lee, \&
Tiffany A. Whittaker (2022). Application of Associative Discrete-Time
Survival Analysis Using Latent Transition Specification.
\emph{Structural Equation Modeling: A Multidisciplinary Journal}.,

\setlength{\leftskip}{0cm}

\textbf{2023}

\setlength{\leftskip}{0.5cm}

\hangindent=2em \hangafter=1 \textbf{Sooyong Lee}, Adam Sales, Hyeon-Ah
Kang, \& Tiffany A. Whittaker (2023). Fully-Latent Principal
Stratification. \emph{The Annual Meeting of the Psychometric Society}
(in print)

\hangindent=2em \hangafter=1 \textbf{Sooyong Lee}, Suhwa Han, \& Seung
W. Choi (2023). Bayesian MIMIC for DIF Detection under Violation of
Equal Variance Assumption. \emph{Educational and Psychological
Measurement} (in review)

\hangindent=2em \hangafter=1 Tiffany A. Whittaker, Laura Stapleton \&
\textbf{Sooyong Lee} (2023). A Tutorial for Obtaining Item Response
Theory Results from Structural Equation Modeling in Mplus Software with
Rating Scales. \emph{Structural Equation Modeling: A Multidisciplinary
Journal} (in review)

\hangindent=2em \hangafter=1 \textbf{Sooyong Lee}, Adam Sales, Hyeon-Ah
Kang, \& Tiffany A. Whittaker (2023). Comparison between Bayesian or ML
in FLPS with Small Sample Sizes. (in progress)

\hangindent=2em \hangafter=1 \textbf{Sooyong Lee}, Adam Sales, Hyeon-Ah
Kang, \& Tiffany A. Whittaker (2023). Multidimensional FLPS. (in
progress)

\setlength{\leftskip}{0cm}

\hypertarget{presentation}{%
\section{Presentation}\label{presentation}}

\setlength{\leftskip}{0cm}

\textbf{Poster}

\setlength{\leftskip}{0.5cm}

\hangindent=2em \hangafter=1 Kejin Lee, \textbf{Sooyong Lee}, \& Youngri
Lee (2018-5). An Alternative Approach to Discrete-Time Survival Analysis
for Meaningful Interpretation. Modern Modeling Methods conference (MMM),
Storrs, CT.

\hangindent=2em \hangafter=1 \textbf{Sooyong Lee} \& Sehee Hong
(2018-7). Exploration of LCA conditions in Latent Class with Low
Proportion. International Meeting of the Psychometric Society (IMPS),
New York, NY.

\hangindent=2em \hangafter=1 \textbf{Sooyong Lee} \& Tiffany A.
Whittaker (2020-4). Comparison of Three Approaches to Class Enumeration
in Growth Mixture Modeling when Time Structures are Variant Across
Latent Classes. American Educational Research Association (AERA),
Virtual.

\hangindent=2em \hangafter=1 \textbf{Sooyong Lee} \& Suhwa Han (2020-7).
Item selection and trait estimation methods in CAT with item leakage.
International Meeting of the Psychometric Society (IMPS), College Park,
MD.

\hangindent=2em \hangafter=1 \textbf{Sooyong Lee}, Suhwa Han, \& Seung
W. Choi (2021-4). DIF Detection with Zero-Inflation under the Mixture
Modeling Framework. American Educational Research Association (AERA),
Virtual.

\setlength{\leftskip}{0cm}

\textbf{Conference presentation}

\setlength{\leftskip}{0.5cm}

\hangindent=2em \hangafter=1 Daniel Lewis \& \textbf{Sooyong Lee}
(2021-4). A Comparison of Two ESS Cut Score Estimation Algorithms.
National Council on Measurement in Education (NCME), Baltimore, MD.

\hangindent=2em \hangafter=1 Garron Gianopulos, Jay Lee, Sangdon Lim,
Luping Niu, \textbf{Sooyong Lee}, \& Seung W. Choi (2022-4). The Impact
of Item Pool Size and Item Pool Distribution on Student Ability
Estimates for a Hybrid Interim-Summative CAT. National Council on
Measurement in Education (NCME), San Diego, USA.

\hangindent=2em \hangafter=1 Jay Lee, M. Christina Schneider, Garron
Gia, Luping Niu, \textbf{Sooyong Lee}, Sangdon Lim, Seung W. Choi
(2022-4). The Impact of Item Pool Size and Item Pool Distribution on
Student Ability Estimates for a Hybrid Interim-Summative CAT. National
Council on Measurement in Education (NCME), San Diego, USA.

\hangindent=2em \hangafter=1 \textbf{Sooyong Lee}, Adam Sales, Hyeon-Ah
Kang, \& Tiffany A. Whittaker (2022-7). Fully-Latent Principal
Stratiication. International Meeting of the Psychometric Society (IMPS),
Bologna, Italy.

\setlength{\leftskip}{0cm}

\hypertarget{program}{%
\section{Program}\label{program}}

\begin{cventries}
    \cventry{}{GRshiny: Graded response model}{Shiny application}{2022}{\begin{cvitems}
\item https://sooyonglee.shinyapps.io/GRShiny/
\end{cvitems}}
    \cventry{}{Embeded Standard Setting}{Shiny application}{2021}{\begin{cvitems}
\item https://sooyonglee.shinyapps.io/ESS\_test/
\end{cvitems}}
    \cventry{}{maat package}{R package}{2022}{\begin{cvitems}
\item https://cran.r-project.org/web/packages/maat/index.html
\end{cvitems}}
    \cventry{}{FLPS package}{R package}{2022}{}\vspace{-4.0mm}
    \cventry{}{clavaan package}{R package}{2023}{}\vspace{-4.0mm}
\end{cventries}

\hypertarget{fellowship-awards}{%
\section{Fellowship \& Awards}\label{fellowship-awards}}

\begin{cventries}
    \cventry{}{William Hays Endowed Fellowship}{Fellowship}{2020-21}{}\vspace{-4.0mm}
    \cventry{}{Benjamin \& Dorothy Fruchter Excellence Award}{Award}{2021-22}{}\vspace{-4.0mm}
\end{cventries}


\label{LastPage}~
\end{document}
