---
name: Sooyong
surname: Lee
position: "PhD"
# profilepic: "img/kate.jpeg"
address: "Educational Psychology, The University of Texas at Austin"
phone: +1 736 865 0618
# www: mariecurie.com
email: "sooyongl09@gmail.com"
# twitter: DontLookUpFilm
github: sooyongl/
# linkedin: mariecurie
aboutme: ""
date: "`r format(Sys.time(), '%B %Y')`"
headcolor: 414141
output: 
  vitae::awesomecv:
    page_total: true
    show_footer: true
# vitae::moderncv:
#   theme: banking
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(here)
library(tidyverse)
library(googlesheets4)
```

```{r functions}
# orcid_data <- do.call("rbind",
#   rorcid::orcid_educations("0000-0002-2140-5352")$`0000-0002-2140-5352`$`affiliation-group`$summaries
# )
# orcid_data %>%
#   detailed_entries(
#     what = `education-summary.role-title`,
#     when = glue::glue("{`education-summary.start-date.year.value`} - {`education-summary.end-date.year.value`}"),
#     with = `education-summary.organization.name`,
#     where = `education-summary.organization.address.city`
#   )

readGoogleSheets <- function(sheet_name) {
  
  cvInfo <- googlesheets4::read_sheet("https://docs.google.com/spreadsheets/d/10ye0YoRjDaCrN4nc1YiFXO8DRtVSyTg1B4z_w8icLtI/edit#gid=0", sheet = sheet_name)
  
  cvInfo
}

```

# Professional Summary

I am a psychometrician with expertise in applying modern statistical theories and techniques. My research interests are in the development and application of statistical models such as such as structural equation modeling (SEM), multilevel modeling (MLM), and item response theory (IRT). Recently, I have focused on Bayesian estimation to model the relationships among variables.


# Education
<!-- I am a Teaching Assistant in the Astronomy Department and am passionate about playing a positive role in shaping the new generation of astronomers.  -->


```{r}
# library(tibble)
# tribble(
#   ~ Degree, ~ Year, ~ Institution, ~ Where,
#   "Informal studies", "1889-91", "Flying University", "Warsaw, Poland",
#   "Master of Physics", "1893", "Sorbonne Université", "Paris, France",
#   "Master of Mathematics", "1894", "Sorbonne Université", "Paris, France"
# ) %>% 
#    detailed_entries(Degree, Year, Institution, Where)
readGoogleSheets("Education") %>% 
  detailed_entries(what = Degree,
                   when = Year,
                   with = Institution,
                   where = Location,
                   why = Details)
```

# Research experience
```{r}
readGoogleSheets("Experience") %>% 
  vitae::detailed_entries(what = note,
                          when = Year,
                          where = Position,
                          with = Name,
                          why = Desc)
```

# Teaching experience
```{r}
readGoogleSheets("Teaching") %>% 
  vitae::detailed_entries(what = note,
                          when = Year,
                          where = Position,
                          with = Name,
                          why = Desc)
```

<!-- # Language skills -->
```{r}
# skills %>% 
#   brief_entries(when = skill) # ,
                # with = level)
```


<!-- \newpage -->


# Publications

```{r}
# library(dplyr)
# knitr::write_bib(c("vitae", "tibble"), "packages.bib")
# 
# bibliography_entries("packages.bib") %>%
#   arrange(desc(author$family), issued)
# 
# bibliography_entries(here("papers.bib")) 
```

<!-- ## Another way to display publications is using R Markdown. You can also use latex commands throughout the document: -->

\setlength{\leftskip}{0cm}
**2021**

\setlength{\leftskip}{0.5cm}
\hangindent=2em
\hangafter=1
Cory L. Cobb, Charles R. Martínez, Jr., **Sooyong Lee**, Tae Kyoung Lee, & Elma I. Lorenzo-Blanco, (2021). Acculturation trajectories differ by youth age at arrival and time in residency among Latino immigrant families in a US emerging immigrant context. *International Journal of Intercultural Relations*,  81, 79-93. <!-- DOI: [10.1016/j.ijintrel.2021.01.005](10.1016/j.ijintrel.2021.01.005).-->

\setlength{\leftskip}{0cm}
**2022**

\setlength{\leftskip}{0.5cm}
\hangindent=2em
\hangafter=1
**Sooyong Lee** & Tiffany A. Whittaker, (2022). Comparison of Three Approaches to Class Enumeration in Growth Mixture Modeling when Time Structures are Variant Across Latent Classes. *Structural Equation Modeling: A Multidisciplinary Journal*,  29,	23-35. <!-- , DOI:[10.1080/10705511.2021.1956320](10.1080/10705511.2021.1956320). -->

\hangindent=2em
\hangafter=1
Seung Choi, Sangdon Lim, Luping Niu, **Sooyong Lee**, Christina M. Schneider, Jay Lee, & Garron J.	(2022).	maat: An R Package for Multiple Administrations Adaptive Testing.	*Applied Psychological Measurement*,	46-1,	73-74. <!-- , DOI:[10.1177/01466216211049212](10.1177/01466216211049212).-->

\hangindent=2em
\hangafter=1
**Sooyong Lee**, Suhwa Han, & Seung W. Choi	(2022).	DIF Detection With Zero-Inflation Under the Factor Mixture Modeling Framework. *Educational and Psychological Measurement*,	82-4,	678-704. <!-- , DOI:[10.1177/00131644211028995](10.1177/00131644211028995).-->

\hangindent=2em
\hangafter=1
**Sooyong Lee** & Tiffany A. Whittaker (2022). Parallel Process Latent Growth Modeling with Multivariate Confounders/Suppressors. *Structural Equation Modeling: A Multidisciplinary Journal*. <!-- , DOI:[10.1080/10705511.2022.2133774](10.1080/10705511.2022.2133774).-->

\hangindent=2em
\hangafter=1
**Sooyong Lee**, Kahyun Lee, & Tiffany A. Whittaker	(2022). Application of Associative Discrete-Time Survival Analysis Using Latent Transition Specification. *Structural Equation Modeling: A Multidisciplinary Journal*., <!-- DOI: [10.1080/10705511.2022.2138892](10.1080/10705511.2022.2138892)-->

\setlength{\leftskip}{0cm}
**2023**

\setlength{\leftskip}{0.5cm}
\hangindent=2em
\hangafter=1
**Sooyong Lee**, Adam Sales, Hyeon-Ah Kang, & Tiffany A. Whittaker (2023).	Fully-Latent Principal Stratification. *The Annual Meeting of the Psychometric Society* (in print)

\hangindent=2em
\hangafter=1
**Sooyong Lee**, Suhwa Han, & Seung W. Choi (2023). Bayesian MIMIC for DIF Detection under Violation of Equal Variance Assumption. *Educational and Psychological Measurement* (in review)

\hangindent=2em
\hangafter=1
Tiffany A. Whittaker, Laura Stapleton & **Sooyong Lee** (2023). A Tutorial for Obtaining Item Response Theory Results from Structural Equation Modeling in Mplus Software with Rating Scales. *Structural Equation Modeling: A Multidisciplinary Journal* (in review)

\hangindent=2em
\hangafter=1
**Sooyong Lee**, Adam Sales, Hyeon-Ah Kang, & Tiffany A. Whittaker (2023).	Comparison between Bayesian or ML in FLPS with Small Sample Sizes. (in progress)

\hangindent=2em
\hangafter=1
**Sooyong Lee**, Adam Sales, Hyeon-Ah Kang, & Tiffany A. Whittaker (2023).	Multidimensional FLPS.  (in progress)

\setlength{\leftskip}{0cm}

# Presentation

```{r}
# readGoogleSheets("Presentation") %>% 
#   filter(category == "poster") %>% 
#   vitae::detailed_entries(what = title,
#                           when = year,
#                           where = Location, 
#                           with = author, 
#                           why = Details)
```

\setlength{\leftskip}{0cm}
**Poster**

\setlength{\leftskip}{0.5cm}
\hangindent=2em
\hangafter=1
Kejin Lee, **Sooyong Lee**, & Youngri Lee (2018-5). An Alternative Approach to Discrete-Time Survival Analysis for Meaningful Interpretation. Modern Modeling Methods conference (MMM), Storrs, CT.

\hangindent=2em
\hangafter=1
**Sooyong Lee** & Sehee Hong (2018-7). Exploration of LCA conditions in Latent Class with Low Proportion. International Meeting of the Psychometric Society (IMPS), New York, NY.

\hangindent=2em
\hangafter=1
**Sooyong Lee** & Tiffany A. Whittaker (2020-4). Comparison of Three Approaches to Class Enumeration in Growth Mixture Modeling when Time Structures are Variant Across Latent Classes. American Educational Research Association (AERA), Virtual.

\hangindent=2em
\hangafter=1
**Sooyong Lee** & Suhwa Han (2020-7). Item selection and trait estimation methods in CAT with item leakage. International Meeting of the Psychometric Society (IMPS), College Park, MD.

\hangindent=2em
\hangafter=1
**Sooyong Lee**, Suhwa Han, & Seung W. Choi (2021-4). DIF Detection with Zero-Inflation under the Mixture Modeling Framework. American Educational Research Association (AERA), Virtual.

\setlength{\leftskip}{0cm}
**Conference presentation**

\setlength{\leftskip}{0.5cm}

\hangindent=2em
\hangafter=1
Daniel Lewis & **Sooyong Lee** (2021-4). A Comparison of Two ESS Cut Score Estimation Algorithms. National Council on Measurement in Education (NCME), Baltimore, MD.

\hangindent=2em
\hangafter=1
Garron Gianopulos, Jay Lee, Sangdon Lim, Luping Niu, **Sooyong Lee**, & Seung W. Choi (2022-4). The Impact of Item Pool Size and Item Pool Distribution on Student Ability Estimates for a Hybrid Interim-Summative CAT. National Council on Measurement in Education (NCME), San Diego, USA.

\hangindent=2em
\hangafter=1
Jay Lee, M. Christina Schneider, Garron Gia, Luping Niu, **Sooyong Lee**, Sangdon Lim, Seung W. Choi (2022-4). The Impact of Item Pool Size and Item Pool Distribution on Student Ability Estimates for a Hybrid Interim-Summative CAT. National Council on Measurement in Education (NCME), San Diego, USA.

\hangindent=2em
\hangafter=1
**Sooyong Lee**, Adam Sales, Hyeon-Ah Kang, & Tiffany A. Whittaker (2022-7). Fully-Latent Principal Stratiication. International Meeting of the Psychometric Society (IMPS), Bologna, Italy.

\setlength{\leftskip}{0cm}

# Program

```{r}
readGoogleSheets("Publication") %>% 
  filter(category == "software") %>% 
  vitae::detailed_entries(
                          # what = title,
                          when = year,
                          where = note,
                          with = author,
                          why = url
                          )
```



# Fellowship & Awards

```{r}
readGoogleSheets("Fellowship/Awards") %>% 
  # filter(category == "poster") %>% 
  vitae::detailed_entries(#what = Type,
                          when = Year,
                          where = Type,
                          with = Desc,
                          # why = Type
                          )
```















