%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for CV/Resume
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Author:
% Claud D. Park <posquit0.bj@gmail.com>
% http://www.posquit0.com
%
%
% Adapted to be an Rmarkdown template by Mitchell O'Hara-Wild
% 23 November 2018
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%
%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[11pt,letterpaper,]{awesome-me}

% Configure page margins with geometry
\usepackage{geometry}
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}


% Specify the location of the included fonts
\fontdir[fonts/]

% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight

\definecolor{awesome}{HTML}{414141}

% Colors for text
% Uncomment if you would like to specify your own color
% \definecolor{darktext}{HTML}{414141}
% \definecolor{text}{HTML}{333333}
% \definecolor{graytext}{HTML}{5D5D5D}
% \definecolor{lighttext}{HTML}{999999}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{true}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}

\def\endfirstpage{\newpage}

%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%-------------------------------------------------------------------------------
% Available options: circle|rectangle,edge/noedge,left/right

\name{Sooyong}{Lee}

\position{PhD}
\address{Educational Psychology, The University of Texas at Austin}

\mobile{+1 737 865 0618}
\email{\href{mailto:sooyongl09@utexas.com}{\nolinkurl{sooyongl09@utexas.com}}}
\orcid{0000-0002-7964-4508}
\github{sooyongl/}

% \gitlab{gitlab-id}
% \stackoverflow{SO-id}{SO-name}
% \skype{skype-id}
% \reddit{reddit-id}


\usepackage{booktabs}

\providecommand{\tightlist}{%
	\setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

%------------------------------------------------------------------------------



% Pandoc CSL macros
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{2em}
\newenvironment{CSLReferences}[3] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
  % set entry spacing
  \ifnum #2 > 0
  \setlength{\parskip}{#2\baselineskip}
  \fi
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{\honortitlestyle{#1}}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{\honordatestyle{#1}}}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

\begin{document}

% Print the header with above personal informations
% Give optional argument to change alignment(C: center, L: left, R: right)
\makecvheader

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
% 2019-02-14 Chris Umphlett - add flexibility to the document name in footer, rather than have it be static Curriculum Vitae


%-------------------------------------------------------------------------------
%	CV/RESUME CONTENT
%	Each section is imported separately, open each file in turn to modify content
%------------------------------------------------------------------------------

\setstretch{1}


\hypertarget{professional-summary}{%
\section{Professional Summary}\label{professional-summary}}

As a psychometrician, I specialize in applying contemporary statistical
theories and techniques to my work. My research interests center around
developing and utilizing statistical models, including structural
equation modeling (SEM), multilevel modeling (MLM), item response theory
(IRT), and mixture modeling. In my recent work, I have placed particular
emphasis on Bayesian estimation as a means of modeling the relationships
between variables.

\hypertarget{education}{%
\section{Education}\label{education}}

\begin{cveducations} \cveducation{Ph.D., Major in Quantitative Methods in Educational Psychology}{The University of Texas at Austin}{Austin, Texas}{2017-Present}{\begin{cvitems}\end{cvitems}}

\cveducation{M.A., Major in Educational Statistics and Measurement}{Korea University}{Seoul, Republic of Korea}{2014-2017}{\begin{cvitems}\end{cvitems}} \end{cveducations}

\vspace{0em}

\hypertarget{research-experience}{%
\section{Research experience}\label{research-experience}}

\begin{cventries} \cventry{}{CGS PhD Career Pathways project}{Graduate Research Assistant}{2018/9-2019/5}{\begin{cvitems}\item Data analysis for surveys to collect data on the career pathways of past and present STEM and humanities PhD students. \end{cvitems}}

\cventry{President's Award for Global Learning (PAGL)}{President's Award for Global Learning (PAGL)}{Graduate Research Assistant}{2019/1-2019/8}{\begin{cvitems}\item Designing a culturally appropriate mobile application to increase mental health literacy and self-care habits among South Korean young adults \end{cvitems}}

\cventry{}{COE Full-Time Tenured and Tenure-Track Faculty}{Graduate Research Assistant}{2019/9-2019/12}{\begin{cvitems}\item Data analysis for surveys of graduate programs of education at the Univerisity of Texas at Austin \end{cvitems}}

\cventry{Northwest Evaluation Association (NWEA)}{maat package development project}{Graduate Research Assistant}{2019/9-2020/5}{\begin{cvitems}\item Development of MAAT package for Computerized Adaptive Testing for Northwest Evaluation Association (NWEA) \end{cvitems}}

\cventry{IES grant}{FLPS project}{Graduate Research Assistant}{2021/9-Present}{\begin{cvitems}\item Development of FLPS package for Fully-latent Principal Stratification \end{cvitems}}

\cventry{Creative Measurement Solutions LLC}{Embedded Standard Setting (ESS)}{Intern}{2020/6-2020/8}{\begin{cvitems}\item Internship for developing Shiny app for Embeded Standard Setting \end{cvitems}}

\cventry{Creative Measurement Solutions LLC}{Embedded Standard Setting (ESS)}{Intern}{2021/6-2021/8}{\begin{cvitems}\item Internship for developing ESS package for Embeded Standard Setting \end{cvitems}} \end{cventries}

\hypertarget{publications}{%
\section{Publications}\label{publications}}

\setlength{\leftskip}{0cm}

\textbf{2021}

\setlength{\leftskip}{0.5cm}

\hangindent=2em \hangafter=1 Cory L. Cobb, Charles R. Martínez, Jr.,
\textbf{Sooyong Lee}, Tae Kyoung Lee, \& Elma I. Lorenzo-Blanco (2021).
Acculturation trajectories differ by youth age at arrival and time in
residency among Latino immigrant families in a US emerging immigrant
context. \emph{International Journal of Intercultural Relations}. 81,
79-93. \url{DOI:10.1016/j.ijintrel.2021.01.005}.

\setlength{\leftskip}{0cm}

\textbf{2022}

\setlength{\leftskip}{0.5cm}

\hangindent=2em \hangafter=1 Seung Choi, Sangdon Lim, Luping Niu,
\textbf{Sooyong Lee}, Christina M. Schneider, Jay Lee, \& Garron J.
(2022). maat: An R Package for Multiple Administrations Adaptive
Testing. \emph{Applied Psychological Measurement}. 46-1, 73-74.
\url{DOI:10.1177/01466216211049212}.

\hangindent=2em \hangafter=1 \textbf{Sooyong Lee}, Suhwa Han, \& Seung
W. Choi (2022). DIF Detection With Zero-Inflation Under the Factor
Mixture Modeling Framework. \emph{Educational and Psychological
Measurement}. 82-4, 678-704. \url{DOI:10.1177/00131644211028995}.

\hangindent=2em \hangafter=1 \textbf{Sooyong Lee} \& Tiffany A.
Whittaker (2022). Comparison of Three Approaches to Class Enumeration in
Growth Mixture Modeling when Time Structures are Variant Across Latent
Classes. \emph{Structural Equation Modeling: A Multidisciplinary
Journal}. 29, 23-35. \url{DOI:10.1080/10705511.2021.1956320}.

\hangindent=2em \hangafter=1 \textbf{Sooyong Lee} \& Tiffany A.
Whittaker (2022). Parallel Process Latent Growth Modeling with
Multivariate Confounders/Suppressors. \emph{Structural Equation
Modeling: A Multidisciplinary Journal}.
\url{DOI:10.1080/10705511.2022.2133774}.

\hangindent=2em \hangafter=1 \textbf{Sooyong Lee}, Kahyun Lee, \&
Tiffany A. Whittaker (2022). Application of Associative Discrete-Time
Survival Analysis Using Latent Transition Specification.
\emph{Structural Equation Modeling: A Multidisciplinary Journal}.
\url{DOI:10.1080/10705511.2022.2138892}.

\hypertarget{program}{%
\section{Program}\label{program}}

\begin{cvsoftwares} \cvsoftware{}{Embeded Standard Setting}{Shiny application}{2021}{\begin{cvitems}\item \url{https://sooyonglee.shinyapps.io/ESS_test/}  \end{cvitems}}

\cvsoftware{}{GRshiny: Graded response model}{Shiny application}{2022}{\begin{cvitems}\item \url{https://sooyonglee.shinyapps.io/GRShiny/}  \end{cvitems}}

\cvsoftware{}{Embeded Standard Setting}{R package}{2022}{\begin{cvitems}\item \url{https://sooyongl.github.io/EmStanS/}  \end{cvitems}}

\cvsoftware{}{maat package}{R package}{2022}{\begin{cvitems}\item \url{https://choi-phd.github.io/maat/}  \end{cvitems}}

\cvsoftware{}{flps package}{R package}{2022}{\begin{cvitems}\item \url{https://sooyongl.github.io/flps/}  \end{cvitems}}

\cvsoftware{}{GRshiny package}{R package}{2023}{\begin{cvitems}\item \url{https://sooyongl.github.io/GRShiny/}  \end{cvitems}}

\cvsoftware{}{clavaan package}{R package}{2023}{\begin{cvitems}\item \url{https://github.com/sooyongl/clavaan}  \end{cvitems}} \end{cvsoftwares}

\vspace{0em}



\end{document}