---
name: Sooyong
surname: Lee
position: "PhD"
address: "Educational Psychology, The University of Texas at Austin"
phone: +1 737 865 0618
email: "sooyongl09@utexas.com"
github: sooyongl/
linestretch: 1
aboutme: ""
date: "`r format(Sys.time(), '%B %Y')`"
fontawesome: yes
papersize: "letterpaper"
headcolor: 414141
orcid: 0000-0002-7964-4508
# csl: apa-cv.csl # change this if you want to use other citation styles
output:
  pdf_document:
    latex_engine: xelatex
    template: "awesome-me.tex"
    keep_tex: true
---
  
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(here)
library(tidyverse)
library(googlesheets4)
library(readxl)
for(R in fs::dir_ls("source")) {source(R)}
```


# Professional Summary

As a psychometrician, I specialize in applying contemporary statistical theories and techniques to my work. My research interests center around developing and utilizing statistical models, including structural equation modeling (SEM), multilevel modeling (MLM), item response theory (IRT), and mixture modeling. In my recent work, I have placed particular emphasis on Bayesian estimation as a means of modeling the relationships between variables.


# Education

```{r results='asis'}

readGoogleSheets("Education") %>% 
  slice(1:2) %>% 
  mk_entry(what = "Degree",
           when = "Year",
           with = "Institution",
           where = "Location",entry_nm = "cveducation")

```

\vspace{0em}

# Research experience

```{r results = 'asis'}
readGoogleSheets("Experience") %>% 
  arrange(desc(Year)) %>% 
  mk_entry(what = "note",
           when = "Year",
           where = "Position",
           with = "Name",
           why = "Desc")
```


# Selective Publications
```{r}
a1 <- readGoogleSheets("Publication") %>%
  filter(type == "article")
```


\setlength{\leftskip}{0.5cm}
```{r results = 'asis'}
a1 %>%
  arrange(desc(year)) %>% 
  filter(str_detect(author, "Choi")) %>% 
  mk_pub(exclude = "doi")
```


# Selective Presentation and Poster
```{r results = 'asis'}
readGoogleSheets("Presentation") %>%
  # filter(type == "presentation") %>%
   filter(str_detect(author, "(Suhwa|Choi|Daniel)")) %>%
  dplyr::arrange(desc(year)) %>% 
    mutate(year = as.character(year),
         year = str_extract(year, "^\\d{4}-\\d{2}")) %>% 
   
  mk_presen()
```

# Program

```{r results = 'asis'}
readGoogleSheets("Software") %>%
  arrange(year) %>% 
  mutate(url = 
           
           paste0("\\url{", url, "} ")
         
  ) %>%
  filter(!str_detect(author, "clavaan")) %>% 
  mk_entry(
    # what = title,
    when = "year",
    where = "note",
    with = "author",
    why = "url",entry_nm = "cvsoftware"
    
  )
```

\vspace{0em}



