%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for CV/Resume
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Author:
% Claud D. Park <posquit0.bj@gmail.com>
% http://www.posquit0.com
%
%
% Adapted to be an Rmarkdown template by Mitchell O'Hara-Wild
% 23 November 2018
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%
%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[11pt,letterpaper,]{awesome-me}

% Configure page margins with geometry
\usepackage{geometry}
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}


% Specify the location of the included fonts
\fontdir[fonts/]

% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight

\definecolor{awesome}{HTML}{414141}

% Colors for text
% Uncomment if you would like to specify your own color
% \definecolor{darktext}{HTML}{414141}
% \definecolor{text}{HTML}{333333}
% \definecolor{graytext}{HTML}{5D5D5D}
% \definecolor{lighttext}{HTML}{999999}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{true}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}

\def\endfirstpage{\newpage}

%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%-------------------------------------------------------------------------------
% Available options: circle|rectangle,edge/noedge,left/right

\name{Sooyong}{Lee}

\position{PhD}
\address{Educational Psychology, The University of Texas at Austin}

\mobile{+1 737 865 0618}
\email{\href{mailto:sooyongl09@gmail.com}{\nolinkurl{sooyongl09@gmail.com}}}
\orcid{0000-0002-7964-4508}
\github{sooyongl/}

% \gitlab{gitlab-id}
% \stackoverflow{SO-id}{SO-name}
% \skype{skype-id}
% \reddit{reddit-id}


\usepackage{booktabs}

\providecommand{\tightlist}{%
	\setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

%------------------------------------------------------------------------------


\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{} % Clear header and footer fields
\fancyfoot[L]{Last Updated: \today} % Left-aligned footer
\fancyfoot[C]{\thepage}
\renewcommand{\headrulewidth}{0pt} % Remove the header rule
\renewcommand{\footrulewidth}{0pt} % Remove the footer rule, if you had one
\fancypagestyle{plain}{\pagestyle{fancy}}

% Pandoc CSL macros
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{2em}
\newenvironment{CSLReferences}[3] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
  % set entry spacing
  \ifnum #2 > 0
  \setlength{\parskip}{#2\baselineskip}
  \fi
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{\honortitlestyle{#1}}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{\honordatestyle{#1}}}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

\begin{document}

% Print the header with above personal informations
% Give optional argument to change alignment(C: center, L: left, R: right)
\makecvheader

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
% 2019-02-14 Chris Umphlett - add flexibility to the document name in footer, rather than have it be static Curriculum Vitae


%-------------------------------------------------------------------------------
%	CV/RESUME CONTENT
%	Each section is imported separately, open each file in turn to modify content
%------------------------------------------------------------------------------

\setstretch{1}


\hypertarget{professional-summary}{%
\section{Professional Summary}\label{professional-summary}}

As a psychometrician, I specialize in applying contemporary statistical
theories and techniques to my work. My research interests center around
developing and utilizing statistical models, including structural
equation modeling (SEM), multilevel modeling (MLM), item response theory
(IRT), and mixture modeling. In my recent work, I have placed particular
emphasis on Bayesian estimation as a means of modeling the relationships
between variables.

\hypertarget{education}{%
\section{Education}\label{education}}

\begin{cveducations} \cveducation{Ph.D., Major in Quantitative Methods in Educational Psychology}{The University of Texas at Austin}{Austin, Texas}{2017-2023}{\begin{cvitems}\item Dissertation: Development of a Method for Addressing Various Censoring Effects in a Latent Growth Curve Modeling Framework. Advisor: Tiffany Whittaker \end{cvitems}}

\cveducation{M.A., Major in Educational Statistics and Measurement}{Korea University}{Seoul, Republic of Korea}{2014-2017}{\begin{cvitems}\item Thesis: Exploration of LCA conditions in Latent Class with Low Proportion. Advisore: Sehee Hong \end{cvitems}} \end{cveducations}

\vspace{-1em}

\hypertarget{publications}{%
\section{Publications}\label{publications}}

\setlength{\leftskip}{0cm}

\textbf{2023}

\setlength{\leftskip}{0.5cm}

\hangindent=2em \hangafter=1 Jonghwan Lee, Christina Schneider, Garron
Gianopulos, Luping Niu, \textbf{Sooyong Lee}, Sangdon Lim, \& Seung W
Choi (2023). The Impact of Item Bank Transition Rules on Student Ability
Estimates and Achievement Level Classifications. \emph{Journal of
Computerized Adaptive Testing}. In print.

\hangindent=2em \hangafter=1 \textbf{Sooyong Lee}, Suhwa Han, \& Seung
W. Choi (2023). Bayesian Moderated Non-linear Factor Analysis for DIF
Detection under Violation of Equal Variance Assumption.
\emph{Educational and Psychological Measurement}. Under review.

\hangindent=2em \hangafter=1 \textbf{Sooyong Lee}, Adam Sales, Hyeon-Ah
Kang, \& Tiffany A. Whittaker (2023). Fully Latent Principal
Stratification With Measurement Models. \emph{Journal of Educational and
Behavioral Statistics}. Under review.

\hangindent=2em \hangafter=1 Rene M. Dailey, \ldots, \& \textbf{Sooyong
Lee} (2023). Testing A Comprehensive Model of Post-Dissolution Distress:
Predicting Initial and Over Time Changes in Distress Following Romantic
Dissolution among U.S. Adults. \emph{Journal of Personality and Social
Psychology}. Under review.

\hangindent=2em \hangafter=1 Kahyun Lee, \textbf{Sooyong Lee}, \&
Allison Master (2023). From Fixed to Growth: An Intensive Longitudinal
Study of the Interplay Between Growth Mindset, Emotions, Sense of
Belonging, and Experiences in Daily Life Among College Students. In
preparation.

\hangindent=2em \hangafter=1 Kahyun Lee, \textbf{Sooyong Lee}, \&
Allison Master (2023). Exploring the Dynamics of Daily Experiences,
Emotions, and ~Depression among Asian American Students: The Moderating
Role of Growth Mindsets. In preparation.

\hangindent=2em \hangafter=1 \textbf{Sooyong Lee}, Adam Sales, Hyeon-Ah
Kang, \& Tiffany A. Whittaker (2023). Bayesian and Maximum Likelihood
Estimation in Fully Latent Principal Stratification. In preparation.

\hangindent=2em \hangafter=1 \textbf{Sooyong Lee}, Adam Sales, Hyeon-Ah
Kang, \& Tiffany A. Whittaker (2023). Multidimensional Fully-latent
Principal Stratification. In preparation.

\hangindent=2em \hangafter=1 \textbf{Sooyong Lee}, Suyoung Kim, \& Jiwon
Kim (2023). Investigating Latent Interaction Effects in Multiple-Group
Analysis in the Structural Equation Modeling Framework. In preparation.

\hangindent=2em \hangafter=1 Tiffany A. Whittaker, Laura Stapleton \&
\textbf{Sooyong Lee} (2023). A Tutorial for Obtaining Item Response
Theory Results from Structural Equation Modeling in Mplus Software with
Rating Scales. In preparation.

\hangindent=2em \hangafter=1 \textbf{Sooyong Lee} \& Tiffany A.
Whittaker (2023). Parallel Process Latent Growth Modeling with
Multivariate Confounders/Suppressors. \emph{Structural Equation
Modeling: A Multidisciplinary Journal}. 30(2), 284-295.

\hangindent=2em \hangafter=1 \textbf{Sooyong Lee}, Kahyun Lee, \&
Tiffany A. Whittaker (2023). Application of Associative Discrete-Time
Survival Analysis Using Latent Transition Specification.
\emph{Structural Equation Modeling: A Multidisciplinary Journal}. 1-12.

\hangindent=2em \hangafter=1 \textbf{Sooyong Lee}, Adam Sales, Hyeon-Ah
Kang, \& Tiffany A. Whittaker (2023). Fully Latent Principal
Stratification: Combining PS with Model-Based Measurement Models..
\emph{The Annual Meeting of the Psychometric Society}. pp.~287-298.

\setlength{\leftskip}{0cm}

\textbf{2022}

\setlength{\leftskip}{0.5cm}

\hangindent=2em \hangafter=1 Seung Choi, Sangdon Lim, Luping Niu,
\textbf{Sooyong Lee}, Christina M. Schneider, Jay Lee, \& Garron J.
(2022). maat: An R Package for Multiple Administrations Adaptive
Testing. \emph{Applied Psychological Measurement}. 46-1, 73-74.
\url{DOI:10.1177/01466216211049212}.

\hangindent=2em \hangafter=1 \textbf{Sooyong Lee}, Suhwa Han, \& Seung
W. Choi (2022). DIF Detection With Zero-Inflation Under the Factor
Mixture Modeling Framework. \emph{Educational and Psychological
Measurement}. 82-4, 678-704. \url{DOI:10.1177/00131644211028995}.

\hangindent=2em \hangafter=1 \textbf{Sooyong Lee} \& Tiffany A.
Whittaker (2022). Comparison of Three Approaches to Class Enumeration in
Growth Mixture Modeling when Time Structures are Variant Across Latent
Classes. \emph{Structural Equation Modeling: A Multidisciplinary
Journal}. 29, 23-35. \url{DOI:10.1080/10705511.2021.1956320}.

\setlength{\leftskip}{0cm}

\textbf{2021}

\setlength{\leftskip}{0.5cm}

\hangindent=2em \hangafter=1 Cory L. Cobb, Charles R. Martínez, Jr.,
\textbf{Sooyong Lee}, Tae Kyoung Lee, \& Elma I. Lorenzo-Blanco (2021).
Acculturation trajectories differ by youth age at arrival and time in
residency among Latino immigrant families in a US emerging immigrant
context. \emph{International Journal of Intercultural Relations}. 81,
79-93. \url{DOI:10.1016/j.ijintrel.2021.01.005}.

\setlength{\leftskip}{0cm}

\textbf{2016}

\setlength{\leftskip}{0.5cm}

\hangindent=2em \hangafter=1 \textbf{Sooyong Lee}, Eun Soo Lee, \& Sehee
Hong (2016). Effects of adolescent's career development on labor market
outcoms: Applying the two0part growth mixture model. \emph{Journal of
Vocational Education \& Training}. 19(3), 137-162.

\hangindent=2em \hangafter=1 Eun Soo Lee, \textbf{Sooyong Lee}, \& Sehee
Hong (2016). The Effects of Community Child-Center Service on School
Adjustment Change Trajectory. \emph{Korean Journal of Social Wellfare
Research}. 50, 59-85.

\setlength{\leftskip}{0cm}

\hypertarget{presentation}{%
\section{Presentation}\label{presentation}}

\setlength{\leftskip}{0cm}

\textbf{Presentation}

\setlength{\leftskip}{0.5cm}

\hangindent=2em \hangafter=1 \textbf{Sooyong Lee}, Adam Sales, Hyeon-Ah
Kang, \& Tiffany A. Whittaker (2024-04). \emph{Multidimensional Fully
Latent Principal Stratification}. American Educational Research
Association (AERA),, Philadelphia, USA.

\hangindent=2em \hangafter=1 Tiffany Whittaker, Hyeon-Ah Kang,
\textbf{Sooyong Lee}, Adam Sales (2023-04). \emph{Bayesian and Maximum
Likelihood Estimation in Fully Latent Principal Stratification}.
National Council on Measurement in Education (NCME), Chicago, USA.

\hangindent=2em \hangafter=1 \textbf{Sooyong Lee}, Adam Sales, Hyeon-Ah
Kang, \& Tiffany A. Whittaker (2022-07). \emph{Fully-Latent Principal
Stratiication}. International Meeting of the Psychometric Society
(IMPS), Bologna, Italy.

\hangindent=2em \hangafter=1 Garron Gianopulos, Jay Lee, Sangdon Lim,
Luping Niu, \textbf{Sooyong Lee}, \& Seung W. Choi (2022-04). \emph{The
Impact of Item Pool Size and Item Pool Distribution on Student Ability
Estimates for a Hybrid Interim-Summative CAT}. National Council on
Measurement in Education (NCME), San Diego, USA.

\hangindent=2em \hangafter=1 Jay Lee, M. Christina Schneider, Garron
Gia, Luping Niu, \textbf{Sooyong Lee}, Sangdon Lim, \& Seung W. Choi
(2022-04). \emph{The Impact of item bank transition rules on student
ability estimates and achievement level classifications}. National
Council on Measurement in Education (NCME), San Diego, USA.

\hangindent=2em \hangafter=1 Daniel Lewis \& \textbf{Sooyong Lee}
(2021-04). \emph{A Comparison of Two ESS Cut Score Estimation
Algorithms}. National Council on Measurement in Education (NCME),
Baltimore, MD, USA.

\setlength{\leftskip}{0cm}

\textbf{Poster}

\setlength{\leftskip}{0.5cm}

\hangindent=2em \hangafter=1 \textbf{Sooyong Lee}, Kahyun Lee, \&
Allison Master (2024-04). \emph{Exploring the dynamics of daily
experiences, emotions, and depression among Asian American students: The
moderating role of growth mindsets.}. American Educational Research
Association (AERA),, Philadelphia, USA.

\hangindent=2em \hangafter=1 \textbf{Sooyong Lee}, Suhwa Han, \& Seung
W. Choi (2021-04). \emph{DIF Detection with Zero-Inflation under the
Mixture Modeling Framework}. American Educational Research Association
(AERA), Virtual.

\hangindent=2em \hangafter=1 \textbf{Sooyong Lee} \& Suhwa Han
(2020-07). \emph{Item selection and trait estimation methods in CAT with
item leakage}. International Meeting of the Psychometric Society (IMPS),
Maryland, USA.

\hangindent=2em \hangafter=1 \textbf{Sooyong Lee} \& Tiffany A.
Whittaker (2020-04). \emph{Comparison of Three Approaches to Class
Enumeration in Growth Mixture Modeling when Time Structures are Variant
Across Latent Classes}. American Educational Research Association
(AERA), Virtual.

\hangindent=2em \hangafter=1 \textbf{Sooyong Lee} \& Sehee Hong
(2018-07). \emph{Exploration of LCA conditions in Latent Class with Low
Proportion}. International Meeting of the Psychometric Society (IMPS),
New York, USA.

\hangindent=2em \hangafter=1 Kejin Lee, \textbf{Sooyong Lee}, \& Youngri
Lee (2018-05). \emph{An Alternative Approach to Discrete-Time Survival
Analysis for Meaningful Interpretation}. Modern Modeling Methods
conference (MMM), Connecticut, USA.

\setlength{\leftskip}{0cm}

\vspace{0em}

\hypertarget{research-experience}{%
\section{Research experience}\label{research-experience}}

\begin{cventries} \cventry{IES grant}{FLPS project}{Post-doc fellow}{2023/9-present}{\begin{cvitems}\item Development of FLPS package for Fully-latent Principal Stratification \end{cvitems}}

\cventry{IES grant}{FLPS project}{Graduate Research Assistant}{2021/9-2023/8}{\begin{cvitems}\item Development of FLPS package for Fully-latent Principal Stratification \end{cvitems}}

\cventry{Creative Measurement Solutions LLC}{Embedded Standard Setting (ESS)}{Intern}{2021/6-2021/8}{\begin{cvitems}\item Internship for developing ESS package for Embeded Standard Setting \end{cvitems}}

\cventry{Creative Measurement Solutions LLC}{Embedded Standard Setting (ESS)}{Intern}{2020/6-2020/8}{\begin{cvitems}\item Internship for developing Shiny app for Embeded Standard Setting \end{cvitems}}

\cventry{Northwest Evaluation Association (NWEA)}{maat package development project}{Graduate Research Assistant}{2019/9-2020/5}{\begin{cvitems}\item Development of MAAT package for Computerized Adaptive Testing for Northwest Evaluation Association (NWEA) \end{cvitems}}

\cventry{}{COE Full-Time Tenured and Tenure-Track Faculty}{Graduate Research Assistant}{2019/9-2019/12}{\begin{cvitems}\item Data analysis for surveys of graduate programs of education at the Univerisity of Texas at Austin \end{cvitems}}

\cventry{President's Award for Global Learning (PAGL)}{President's Award for Global Learning (PAGL)}{Graduate Research Assistant}{2019/1-2019/8}{\begin{cvitems}\item Designing a culturally appropriate mobile application to increase mental health literacy and self-care habits among South Korean young adults \end{cvitems}}

\cventry{}{CGS PhD Career Pathways project}{Graduate Research Assistant}{2018/9-2019/5}{\begin{cvitems}\item Data analysis for surveys to collect data on the career pathways of past and present STEM and humanities PhD students. \end{cvitems}} \end{cventries}

\vspace{0em}

\hypertarget{teaching-experience}{%
\section{Teaching experience}\label{teaching-experience}}

\begin{cventries} \cventry{Professor Tiffany Whittaker}{EDP 380C: Structural Equation Modeling}{Teaching Assistant}{2021/1-2021/5}{\begin{cvitems}\end{cvitems}}

\cventry{Professor Tiffany Whittaker}{EDP 380C: Structural Equation Modeling}{Teaching Assistant}{2020/1-2020/5}{\begin{cvitems}\end{cvitems}} \end{cventries}

\hypertarget{program}{%
\section{Program}\label{program}}

\begin{cvsoftwares} \cvsoftware{}{GRshiny package}{R package}{2023}{\begin{cvitems}\item \url{https://sooyongl.github.io/GRShiny/}  \end{cvitems}}

\cvsoftware{}{clavaan package}{R package}{2023}{\begin{cvitems}\item \url{https://github.com/sooyongl/clavaan}  \end{cvitems}}

\cvsoftware{}{GRshiny: Graded response model}{Shiny application}{2022}{\begin{cvitems}\item \url{https://sooyonglee.shinyapps.io/GRShiny/}  \end{cvitems}}

\cvsoftware{}{Embeded Standard Setting}{R package}{2022}{\begin{cvitems}\item \url{https://sooyongl.github.io/EmStanS/}  \end{cvitems}}

\cvsoftware{}{maat package}{R package}{2022}{\begin{cvitems}\item \url{https://choi-phd.github.io/maat/}  \end{cvitems}}

\cvsoftware{}{flps package}{R package}{2022}{\begin{cvitems}\item \url{https://cran.r-project.org/web/packages/flps/index.html}  \end{cvitems}}

\cvsoftware{}{Embeded Standard Setting}{Shiny application}{2021}{\begin{cvitems}\item \url{https://sooyonglee.shinyapps.io/ESS_shiny/}  \end{cvitems}} \end{cvsoftwares}

\vspace{0em}

\hypertarget{service}{%
\section{Service}\label{service}}

\begin{cventries} \cventry{}{International Journal of Intercultural Relations}{Reviewer}{2023/7 - present}{\begin{cvitems}\end{cvitems}} \end{cventries}

\hypertarget{fellowship-awards}{%
\section{Fellowship \& Awards}\label{fellowship-awards}}

\begin{cvhonors} \cvhonor{}{Benjamin \& Dorothy Fruchter Excellence Award}{Award}{2021-22}{\begin{cvitems}\end{cvitems}}

\cvhonor{}{William Hays Endowed Fellowship}{Fellowship}{2020-21}{\begin{cvitems}\end{cvitems}} \end{cvhonors}



\end{document}