---
output: 
  pdf_document:
    latex_engine: xelatex
    includes:
      in_header: preamble.tex
fontsize: 10pt
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  results='asis', echo = FALSE, warning = FALSE, message = FALSE)

library(glue)
library(tidyverse)
library(readxl)

# for(R in fs::dir_ls("source/new_make.R")) {source(R)}
source("../source/new_make.R")
source("../source/read_GoogleSheets.R")

# Latex code generators functions
header1 <- function(title) {
  title <- str_replace_all(title, fixed("&"), "\\&")
  
  glue("
\\noindent\\colorbox{lightergrey}{%
    \\parbox{\\dimexpr\\textwidth-2\\fboxsep\\relax}{%
        \\centering
        \\fontspec{Arial} \\textbf{\\Large <<title>>}%
    }%
}\\medskip", .open = "<<", .close = ">>")
}

header2 <- function(title) {
  title <- str_replace_all(title, fixed("&"), "\\&")
  
  glue("
\\begin{flushleft}
  \\fontspec{Arial}
  \\textbf{\\large <<title>>} 
\\end{flushleft} ", 
.open = "<<", .close = ">>")
}


one_entry <- function(a1) {
  
  a1 <- str_replace_all(a1, fixed("&"), "\\&")
  a1 <- str_replace(a1, fixed("Sooyong Lee"), '\\textbf{Sooyong Lee}')
  
  glue("<<a1>>
       
       ", 
       .open = "<<", .close = ">>")
}


two_entry <- function(a1, a2, width = c(0.2, 0.8)) {
  
  a1 <- str_replace_all(a1, fixed("&"), "\\&")
  a2 <- str_replace_all(a2, fixed("&"), "\\&")
  
  glue("
\\begin{tabular}{p{<<width[1]>>\\textwidth} p{<<width[2]>>\\textwidth} }

  \\textbf{<<a1>>} & <<a2>>

\\end{tabular}
\\smallskip

", 
.open = "<<", .close = ">>")
}

three_entry <- function(a1, a2, a3) {
  
  a1 <- str_replace_all(a1, fixed("&"), "\\&")
  a2 <- str_replace_all(a2, fixed("&"), "\\&")
  
  glue("
\\begin{tabular}{p{0.2\\textwidth} p{0.6\\textwidth} p{0.2\\textwidth} }

  \\textbf{<<a1>>} & <<a2>> & <<a3>> \\

\\end{tabular}

", 
.open = "<<", .close = ">>")
}

```

<!-- My info -->
```{r}
maketitle <- function(name, position, institute, contact) {
  
  name <- str_replace_all(name, fixed("&"), "\\&")
  position <- str_replace_all(position, fixed("&"), "\\&")
  institute <- str_replace_all(institute, fixed("&"), "\\&")
  
  glue("\\centering \\textbf{\\Large <<name>>}

\\centering <<position>>

\\centering <<institute>>

\\centering <<contact>>", .open = "<<", .close = ">>")
  
}

maketitle("Sooyong Lee, Ph.D.", 
          "Psychometrician", 
          "WIDA\n\nThe University of Wisconsin-Madison",
          "\\faEnvelope: sooyongl09@gmail.com | \\orcid{0000-0002-7964-4508}: 0000-0002-7964-4508 | \\aiGoogleScholar\\href{https://scholar.google.com/citations?user=XIoJogsAAAAJ&hl=ko&oi=sra}{Google Scholar} | \\faGithub: sooyongl/")



```

`r header1("PROFESSIONAL SUMMARY")`

\begin{flushleft}
As a psychometrician, I specialize in applying contemporary statistical theories and techniques to my work. My research interests center around developing and utilizing statistical models, including structural equation modeling (SEM), multilevel modeling (MLM), item response theory (IRT), and mixture modeling. In my recent work, I have placed particular emphasis on Bayesian estimation as a means of modeling the relationships between variables.
\end{flushleft}

<!-- `r header1("CONTACTS OF REFERENCES")` -->

<!-- \begin{tabular}{p{0.4\textwidth}@{\hspace{-10pt}}@{}p{0.4\textwidth}@{\hspace{-10pt}}@{}p{0.3\textwidth} } -->

<!-- 1.	\textbf{Tiffany A. Whittaker} -->

<!-- Professor -->

<!-- The University of Texas at Austin   -->

<!-- Department of Educational Psychology -->

<!-- Quantitative Methods -->

<!-- \textbf{Email}: t.whittaker@austin.utexas.edu -->

<!-- \textbf{Phone}: 512-471-2749     & -->

<!-- 2.	\textbf{Seung W. Choi} -->

<!-- Professor -->

<!-- The University of Texas at Austin   -->

<!-- Department of Educational Psychology -->

<!-- Quantitative Methods -->

<!-- \textbf{Email}: schoi@austin.utexas.edu -->

<!-- \textbf{Phone}: 512-471-2751 & -->

<!-- 3.	\textbf{Cory L. Cobb} -->

<!-- Assistant Professor -->

<!-- Texas A\&M University -->

<!-- School of Public Health -->

<!-- Department of Health Behavior -->


<!-- \textbf{Email}: cory.cobb@tamu.edu -->

<!-- \textbf{Phone}: 501-749-3382 -->

<!-- \end{tabular} -->


<!-- My Education-->
`r header1("EDUCATION")`

```{r}
edu_entry <- function(year, position, school, location, Details) {
  
  year <- str_replace_all(year, fixed("&"), "\\&")
  position <- str_replace_all(position, fixed("&"), "\\&")
  school <- str_replace_all(school, fixed("&"), "\\&")
  location <- str_replace_all(location, fixed("&"), "\\&")
  
  glue("
\\begin{tabular}{p{0.15\\textwidth}@{\\hspace{-10pt}}@{}p{0.85\\textwidth}  }
  \\textbf{<<year>>} & <<position>> \\\\\\
                     & <<school>>,  <<location>>  \\\\\\
                     &  \\multicolumn{1}{p{0.85\\textwidth}}{- <<Details>>}   \\\\\\

\\end{tabular}

", 
.open = "<<", .close = ">>")
}

readGoogleSheets("Education") %>% 
  mutate_all(~ case_when(is.na(.x) ~ " ", TRUE ~ .x)) %>% 
  # slice(1:2) %>% 
  mutate(
    # Details = str_replace(Details, "Advi", " \\\\nAdvi"),
    # Institution = glue("{Institution}, {Location}"),
    tex = edu_entry(Year, Degree, Institution, Location, Details)
  ) %>% 
  pull(tex)


```

<!-- `r header1("RESEARCH INTERESTS")` -->



\par\bigskip

<!-- My Research-->
`r header1("PUBLICATIONS")`


```{r eval = T, echo = F, results = 'hide'}
pub_entry <- function(number, year, name, title, journal, page) {
  
  year <- str_replace_all(year, fixed("&"), "\\&")
  name <- str_replace_all(name, fixed("&"), "\\&")
  title <- str_replace_all(title, fixed("&"), "\\&")
  journal <- str_replace_all(journal, fixed("&"), "\\&")
  page <- str_replace_all(page, fixed("&"), "\\&")
  
  name <- str_replace_all(name, fixed("Sooyong Lee"), "\\textbf{Sooyong Lee}")
  
  glue("
\\begin{tabular}{p{0.05\\textwidth} p{0.95\\textwidth} }

  <<number>> & {\\hangindent=1.5em \\hangafter=1 
  <<name>>. (<<year>>). <<title>>. \\emph{<<journal>>}, <<page>> }

\\end{tabular}", 
.open = "<<", .close = ">>")
  
  # 1. **2023** Sooyong Lee, Kahyun Lee & Tiffany A. Whittaker. *Application of Associative Discrete-Time Survival Analysis Using Latent Transition Specification*. Structural Equation Modeling: A Multidisciplinary Journal, 1-12.
}

a1 <- readGoogleSheets("Publication") %>%
  filter(type == "article")
# 
temp <- a1 %>%
  # filter(year == "2023") %>%
  # mk_pub_new(exclude = "doi") %>%
   mk_pub_new() %>%
  mutate(
    number = row_number(),
    out = two_entry('-', out, c(0.01, 0.99))
  )

```


\begin{flushleft} \textbf{In Preparation} \end{flushleft}

```{r}
temp %>% 
  filter(str_detect(note, "preparation")) %>% 
  filter(year == "2025") %>%
  pull(out)

```


\begin{flushleft} \textbf{Under Review} \end{flushleft}

```{r}
temp %>% 
  filter(str_detect(note, "review")) %>% 
  filter(year == "2025") %>%
  pull(out)

```
\newpage 

<!-- My Research-->
`r header1("PUBLICATIONS")`


\begin{flushleft} \textbf{2025} \end{flushleft}
<!-- \setlength{\leftskip}{0.5cm} -->

```{r}
temp %>% 
  filter(!str_detect(note, "preparation|review")) %>% 
  filter(year == "2025") %>%
  filter(!str_detect(title, "Development of a Method for Handling|DIF Detection With Zero| ABayesian Moderated Nonlinear Factor Analysis|Fully Latent Principal Stratification With| Comparison of Three Approaches to Class")) %>% 
  pull(out)


# Gianopulos, G., Lee, J., Lim, S., Niu, L., Lee, S., & Choi, S. W. (in press). The impact of item pool size and item pool distribution on student ability estimates for a hybrid interim-summative CAT. Journal of Computerized Adaptive Testing.

# Lee, J., Lim, S., Schneider, M. C., Gianopulos, G., Niu, L., Lee, S., & Choi, S. W. (in press). The impact of item bank transition rules on student ability estimates and achievement level classifications. Journal of Computerized Adaptive Testing.

```


\begin{flushleft} \textbf{2024} \end{flushleft}


```{r}
temp %>% 
  filter(year == "2024") %>%
    filter(!str_detect(title, "Development of a Method for Handling|DIF Detection With Zero|A Bayesian Moderated Nonlinear Factor Analysis|Fully Latent Principal Stratification With|Comparison of Three Approaches to Class")) %>% 
  pull(out)

```

\begin{flushleft} \textbf{2023} \end{flushleft}

```{r}
temp %>% 
  filter(year == "2023") %>%
    filter(!str_detect(title, "Development of a Method for Handling|DIF Detection With Zero|A Bayesian Moderated Nonlinear Factor Analysis|Comparison of Three Approaches to Class")) %>% 
  pull(out)

```


\begin{flushleft} \textbf{2022} \end{flushleft}

```{r}
temp %>% 
  filter(year == "2022") %>%
    filter(!str_detect(title, "Development of a Method for Handling|DIF Detection With Zero|A Bayesian Moderated Nonlinear Factor Analysis|Fully Latent Principal Stratification With|Comparison of Three Approaches to Class")) %>% 
  pull(out)

```


\begin{flushleft} \textbf{2021} \end{flushleft}

```{r}
temp %>% 
  filter(year == "2021") %>%
    filter(!str_detect(title, "Development of a Method for Handling|DIF Detection With Zero| ABayesian Moderated Nonlinear Factor Analysis|Fully Latent Principal Stratification With| Comparison of Three Approaches to Class")) %>% 
  pull(out)

```


\newpage 

\begin{flushleft} \textbf{2020} and earlier \end{flushleft}

```{r}
temp %>% 
  filter(year %in% c("2020","2019","2018","2017","2016")) %>%
  pull(out)

```

\setlength{\leftskip}{0cm}
\par\bigskip

<!-- \vspace{10em} -->

`r header1("NATIONAL AND INTERNATIONAL PRESENTATIONS")`

\begin{flushleft} \textbf{Presentations} \end{flushleft}

```{r results = 'asis'}
readGoogleSheets("Presentation") %>%
  filter(type == "presentation") %>% 
  dplyr::arrange(desc(year)) %>% 
  mutate(number = row_number()) %>% 
  mutate(
    year = as.character(year),
    year = str_extract(year, "^\\d{4}-\\d{2}"),
    number = row_number(),
    out = one_entry(glue("{number}. {author} ({year}). {title}. {conference}, {location}."))
  ) %>% 
  pull(out)
```

\begin{flushleft} \textbf{Posters} \end{flushleft}

```{r results = 'asis'}
readGoogleSheets("Presentation") %>%
  filter(type == "poster") %>% 
  dplyr::arrange(desc(year)) %>%
  mutate(number = row_number()) %>% 
  mutate(
    year = as.character(year),
    
    year = str_extract(year, "^\\d{4}-\\d{2}"),
    number = row_number(),
    out = one_entry(glue("{number}. {author} ({year}). {title}. {conference}, {location}."))
  ) %>% 
  pull(out)
```

`r header1("RESEARCH")`

```{r results = 'asis'}
research_entry <- function(a1, a2, a3, a4) {
  glue("
\\begin{tabular}{p{0.2\\textwidth}@{\\hspace{-10pt}}@{}p{0.6\\textwidth} p{0.2\\textwidth} }

  <<a1>> & <<a2>> & <<a3>> \\\\\\
         &  \\multicolumn{2}{p{0.7\\textwidth}}{- <<a4>>}   \\\\\\

\\end{tabular}

", 
.open = "<<", .close = ">>")
}

readGoogleSheets("Experience") %>%
  dplyr::arrange(desc(Year)) %>%
  mutate(
    out = research_entry(Position, Name, Year, Desc)
  ) %>% pull(out)

```


\par\bigskip

`r header1("TEACHING")`

`r header2("Teaching Assistant")`

University of Texas at Austin

```{r results = 'asis'}
teaching_entry <- function(Year, Position, Name, note, Desc) {
  
  
  glue("
\\begin{tabular}{p{0.8\\textwidth} p{0.2\\textwidth}  }

  <<Name>> & <<Year>>  \\\\\\
  <<note>> &   \\\\\\

\\end{tabular}

", 
.open = "<<", .close = ">>")
}


readGoogleSheets("Teaching") %>%
    dplyr::arrange(desc(Year)) %>%
  mutate(
    Desc = "Univeristy of Texas at Austin",
    out = teaching_entry(Year, Position, Name, note, Desc)
  ) %>% 
  pull(out)
```

`r header1("PROGRAMS")`

```{r results = 'asis'}
software_entry <- function(type, year, name, title, what, link) {
  name <- str_replace(name, fixed("Sooyong Lee"), '\\textbf{Sooyong Lee}')
  
  glue("
\\begin{tabular}{p{0.2\\textwidth}@{\\hspace{-10pt}}@{}p{0.7\\textwidth} p{0.1\\textwidth} }

  <<type>> & <<title>> & <<year>> \\\\\\
         &  <<name>> &   \\\\\\

\\end{tabular}

", 
.open = "<<", .close = ">>")
}


readGoogleSheets("Software") %>%
  mutate(url = if_else(is.na(url), "", url)) %>% 
  dplyr::arrange(desc(year)) %>% 
  mutate(url = paste0("\\url{", url, "} "),
         # author = paste0(author, "\n", url),
         out = software_entry(note, year, url, author, "", "")
  ) %>%
  pull(out)

```

`r header1("SERVICE")`


```{r results = 'asis'}
readGoogleSheets("Service") %>%
   dplyr::arrange(desc(Year)) %>% 
  mutate(
    out = three_entry(Position, Name, Year)
  ) %>% 
  pull(out)

```

<!-- My Past Relevant Positions-->

```{r}
# header1("Academic Appointment & Past Relevant Positions")
```

```{r}
# two_entry(a1 = "2011-present", 
#           a2 = "Assistant Professor, Psychological Health & Learning Sciences, College of Education, University of Houston")
# 
# three_entry(a1 = "2011-present", 
#           a2 = "Assistant Professor, Psychological Health & Learning Sciences, College of Education",
#           a3 = "University of Houston")
```


```{r}
# header1("Military Experience")
# 
# Leadership Rank: Sergeant
# Honorable discharge – 2009
# Army of Republic of Korea
# [10, 2007] – [09, 2009]
```






