---
output:
  pdf_document:
    latex_engine: xelatex
    includes:
      in_header: preamble.tex
# header-includes:
#   - \usepackage{fontspec}
#   - \usepackage{xeCJK}
#   - \usepackage{fontawesome5}
#   - \usepackage{academicons}
#   - \setmainfont{Arial}
#   - \setCJKmainfont{Malgun Gothic}
#   - \usepackage{hyperref}
#   - \newcommand{\orcid}[1]{\href{https://orcid.org/#1}{\textcolor[HTML]{A6CE39}{\aiOrcid}}}
#   - \definecolor{lightergrey}{gray}{0.9}

# output: 
#   latex_document:
#     latex_engine: xelatex
#     includes:
#       in_header: preamble.tex
# format:
#   pdf:
#     pdf-engine: xelatex
#     include-in-header: preamble.tex
#     keep-tex: true
fontsize: 10pt
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  results='asis', echo = FALSE, warning = FALSE, message = FALSE)

library(glue)
library(tidyverse)
library(readxl)

# for(R in fs::dir_ls("source/new_make.R")) {source(R)}
source("../source/new_make.R")
source("../source/read_GoogleSheets.R")

# Latex code generators functions
header1 <- function(title) {
  title <- str_replace_all(title, fixed("&"), "\\&")
  
  glue("
\\noindent\\colorbox{lightergrey}{%
    \\parbox{\\dimexpr\\textwidth-2\\fboxsep\\relax}{%
        \\centering
        \\fontspec{Arial} \\textbf{\\Large <<title>>}%
    }%
}\\medskip", .open = "<<", .close = ">>")
}

header2 <- function(title) {
  title <- str_replace_all(title, fixed("&"), "\\&")
  
  glue("
\\begin{flushleft}
  \\fontspec{Arial}
  \\textbf{\\large <<title>>} 
\\end{flushleft} ", 
.open = "<<", .close = ">>")
}


one_entry <- function(a1) {
  
  a1 <- str_replace_all(a1, fixed("&"), "\\&")
  a1 <- str_replace(a1, fixed("Sooyong Lee"), '\\textbf{Sooyong Lee}')
  
  glue("<<a1>>
       
       ", 
       .open = "<<", .close = ">>")
}


two_entry <- function(a1, a2, width = c(0.2, 0.8)) {
  
  a1 <- str_replace_all(a1, fixed("&"), "\\&")
  a2 <- str_replace_all(a2, fixed("&"), "\\&")
  
  glue("
\\begin{tabular}{p{<<width[1]>>\\textwidth} p{<<width[2]>>\\textwidth} }

  \\textbf{<<a1>>} & <<a2>>

\\end{tabular}
\\smallskip

", 
.open = "<<", .close = ">>")
}

three_entry <- function(a1, a2, a3) {
  
  a1 <- str_replace_all(a1, fixed("&"), "\\&")
  a2 <- str_replace_all(a2, fixed("&"), "\\&")
  
  glue("
\\begin{tabular}{p{0.2\\textwidth} p{0.6\\textwidth} p{0.2\\textwidth} }

  \\textbf{<<a1>>} & <<a2>> & <<a3>> \\

\\end{tabular}

", 
.open = "<<", .close = ">>")
}

```

<!-- My info -->
```{r}
maketitle <- function(name, position, institute, contact) {
  
  name <- str_replace_all(name, fixed("&"), "\\&")
  position <- str_replace_all(position, fixed("&"), "\\&")
  institute <- str_replace_all(institute, fixed("&"), "\\&")
  
  glue("\\centering \\textbf{\\Large <<name>>}

\\centering <<position>>

\\centering <<institute>>

\\centering <<contact>>", .open = "<<", .close = ">>")
  
}

maketitle("Sooyong Lee, Ph.D.",
          "Psychometrician",
          "WIDA\n\nThe University of Wisconsin-Madison",
          "\\faEnvelope: sooyongl09@gmail.com | \\orcid{0000-0002-7964-4508}: 0000-0002-7964-4508 | \\aiGoogleScholar\\href{https://scholar.google.com/citations?user=XIoJogsAAAAJ&hl=ko&oi=sra}{Google Scholar} | \\faGithub: sooyongl/")



```


<!-- \includegraphics[width=3cm,height=4cm,keepaspectratio]{../img/selfi.jpg} -->

`r header1("PROFESSIONAL SUMMARY")`

\begin{flushleft}
As a psychometrician, I specialize in applying contemporary statistical theories and techniques to my work. My research interests center around developing and utilizing statistical models, including structural equation modeling (SEM), multilevel modeling (MLM), item response theory (IRT), and mixture modeling. In my recent work, I have placed particular emphasis on Bayesian estimation as a means of modeling the relationships between variables.
\end{flushleft}

`r header1("CONTACTS OF REFERENCES")`

\begin{tabular}{p{0.4\textwidth}@{\hspace{-10pt}}@{}p{0.4\textwidth}@{\hspace{-10pt}}@{}p{0.3\textwidth} }

1.	\textbf{Tiffany A. Whittaker}

Professor

The University of Texas at Austin

Department of Educational Psychology

Quantitative Methods

\textbf{Email}: t.whittaker@austin.utexas.edu

\textbf{Phone}: 512-471-2749     &

2.	\textbf{Seung W. Choi}

Professor

The University of Texas at Austin

Department of Educational Psychology

Quantitative Methods

\textbf{Email}: schoi@austin.utexas.edu

\textbf{Phone}: 512-471-2751 &

3.	\textbf{Cory L. Cobb}

Assistant Professor

Texas A\&M University

School of Public Health

Department of Health Behavior


\textbf{Email}: cory.cobb@tamu.edu

\textbf{Phone}: 501-749-3382

\end{tabular}


한글이 적용되는지